Multi-Agent Reinforcement Learning in Zombie-Survival Games

### 2020-12-20 paper/paper.tex
update paper and schenario code comments

We found that if we accept the model then survivors are learning that if they can hit an agent, a survivor is higher value target than a zombie (Figure \ref{fig:survivor_skill}, plot 5).
We were unable to train the model for more than 20,000 episodes (due to time constraints) to determine if defection emerges as a dominant strategy over time.

@@

In attempting to design scenarios to model a `real-life' zombie-survival situation we witnessed the emergence of surprising behaviors.
In each case, our surprise was a result of the environment's dynamics (as implemented) not matching our expectations.

In the \emph{baseline} scenario, we didn't expect target-fixation because our personal state-space representation was already abstracting the agents into two teams.
When we aligned the state-space using our personal abstractions in the \emph{anonymous} scenario the behavior was corrected, but we encountered further surprises.
We did not expect the wall-bouncing strategy because our personal expectation was that running into a wall when chased by zombies is counterproductive.

Our explanation for this assumption was to do with health, which we weren't modelling.
Once we corrected this in the \emph{health} scenario the strategy became less common and we observed the behavior we expected.

In the \emph{armed} scenario we weren't certain how agents would respond.
Survivors were less effective than expected within the training time at using weapons, likely because we underestimated the complexities of a task achievable by humans (in popular depictions of zombie-survivor scenarios, survivors are adept at shooting).
The social dilemma presented warrants further study;
a more thorough empirical game theoretic analysis such as performed in \citealp{10.5555/3091125.3091194} would be an interesting exercise.

We found it an interesting challenge to attempt to produce desired behavior in a multi-agent setting.
Above all, we learned that agents will seek to maximize their reward functions, rather than do what you expect them to do.

>>>>

We found that if we accept the model then survivors are learning that if they can hit an agent, it is more valuable to hit a survivor (Figure \ref{fig:survivor_skill}, plot 5).
We were unable to train the model for more than 20,000 episodes (due to time constraints) to determine if defection emerges as a dominant strategy over time.

@@

In attempting to design scenarios to model a `real-life' zombie-survival situation we encountered unexpected agent policies.
We did not expect target-fixation, wall-bouncing or survivors having trouble using weapons.

When we encoded additional dynamics into the environment to make our expectations explicit we caused changes in agent policy; only some of these changes were successful.
Altering an environment and modifying the state-space as we have done is one way to elicit desired policies,
another approach is modifying the reward function to add detail and caveats to the agent's high-level goal.
Both methods look to be blunt instruments for a real-world setting.

An implication of the challenges we saw is that if an RL agent were to be deployed in a real-world environment,
the agent's behavior may only be consistent with expectations to the extent that the environment dynamics remain stationary.
Beyond the known environmental dynamics, it is hard to know ahead of time (without modelling and simulation) what agent behavior would result.
Additionally, policies learned are not Bayes-optimal, so an agent may not always learn a desired policy even in the presence of a well expressed reward function and a perfectly representative simulation environment.

One can make the argument that all real-world environments are multi-agent settings,
so the study of multi-agent learning dynamics is especially interesting for real-world applications.

A potential avenue for further exploration of the Zombie-Survival game
would be a more thorough, empirical game-theoretic analysis, such as undertaken in \citealp{10.5555/3091125.3091194}.

We found it an interesting challenge to attempt to produce desired behavior in a multi-agent setting.
While we had some success, we would hesitate before deploying our agents into the real world.
